### 2011-01-26 paper/learningMethods.tex
Few edits

The first method is to choose a family of \emph{parametrized functions}.  By fixing the parameters to a particular set of values, we obtain a deterministic motion function over time.  We tried several parametrizations on the robot and, obtaining reasonble early success, settled on one particular parametrization.  We dubbed this the \emph{SineModel5}, as it has five parameters and employs a sine wave as its root pattern.

@@

1) The value for $\vec{\theta}$ for the initial trial, and
2) The next value of $\vec{\theta}$ to try, given the $\vec{\theta}$ and $f(\vec{\theta})$ for all previous trials

>>>>

The first method is to choose a family of \emph{parametrized
  functions}.  By fixing the parameters to a particular set of values,
we obtain a deterministic motion function over time.  We tried several
parametrizations on the robot and, upon obtaining reasonable early
success, settled on one particular parametrization.  We dubbed this
the \emph{SineModel5}, as it has five parameters and employs a sine
wave as its root pattern.

@@

1) The value for $\vec{\theta}$ for the initial trial, and

2) The next value of $\vec{\theta}$ to try, given the $\vec{\theta}$
and $f(\vec{\theta})$ for all previous trials

### 2011-01-26 paper/problemDefinition.tex
Few edits

Mathematically, we define a gait as a function that specifies
a vector of commanded motor positions for a robot over time.
%Using this definition, we require one function per motor.
We can write gaits without feedback --- also called feed forward gaits
--- as

@@

\noindent for some measurement vector $\vec{z}$.  Though perhaps obvious, it
is worth noting that feedforward gaits are deterministic (unless they
include random elements), producing the same command pattern each time
they are run.  The output of a gait that includes feedback, on the
other hand, depends on the actual measurements, and noise in these
measurements may result in different $\vec{x}$ values each time they are
run.

>>>>

Mathematically, we define a gait as a function that specifies
a vector of commanded motor positions for a robot over time.
%Using this definition, we require one function per motor.
We can write gaits without feedback --- also called feedforward gaits
--- as

@@

\noindent for some measurement vector $\vec{z}$.  Feedforward gaits
are deterministic (unless they include random elements), so they
produce the same command pattern each time they are run.  While the
commanded positions will be the same from trial to trial, the actual
robot motion and measured fitness will vary due to the noisiness of
trials in the real world.

The output of a gait that includes feedback, on the other hand,
depends on the actual measurements, and noise in these measurements
may result in different $\vec{x}$ values each time they are run.
